---
title: "ER Wait times at ABC Hospital Chain"
subtitle: "Analyzing the wait times"
author: "Sai Valluri"
date: "`r Sys.Date()`"
output:
  tufte::tufte_handout:
    citation_package: natbib
    latex_engine: xelatex
  tufte::tufte_book:
    citation_package: natbib
    latex_engine: xelatex
bibliography: skeleton.bib
link-citations: yes
geometry: margin = 0.5in
---

```{r setup, include=FALSE}
# Required libraries
library(tufte)
library(knitr)
library(pander)
# invalidate cache when the tufte version changes
knitr::opts_chunk$set(tidy = FALSE, cache.extra = packageVersion('tufte'))
options(htmltools.dir.version = FALSE)
setwd("/Users/saivalluri/Desktop/SV11/class 2/ANOVA/ERWaiting/data/")
source ("HW.R")
```

# Introduction
This document provides the Descriptive Statistics of the Mean Wait Times in ABC Hospital's Main and three of it's Sattelite Campuses. 

```{r, echo=FALSE}
kable(ER)

```

# Descriptive Statistics
```{r, echo=FALSE}
pandoc.table(ER,style = "simple",caption = "Descriptive Statistics")
```
# ANOVA
The ANOVA test was conducted to determine if there is any statistical difference between the mean wait times between the four campuses. 
The calculation below shows a p-Value of 0.000859. Thus, we reject the Null Hypotheses. We can say with 95% confidence level that the Mean ER Wait times in the four campuses are not the same. 
```{r, echo=FALSE}
pander(ER.aov.summary)
```
# Tukey-Kramer test
```{r, echo=FALSE}
pander(ER.tukey)
```
# Levene Test
```{r, echo=FALSE}
pander(ER.levene)
```
# Boxplot
```{r, echo=FALSE}
plot(bp)
```
# f Distribution
```{r, fig.width=4,fig.height=3, echo=FALSE}
plot(pf)
```